### 2014-10-01 Paper1/paper1.tex
Updated-ish

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

@@

% Bold the 'Figure #' in the caption and separate it with a period
% Captions will be left justified
\usepackage[labelfont=bf,labelsep=period,justification=raggedright]{caption}
\usepackage[noperiod]{jabbrv}
% Use the PLoS provided bibtex style
\bibliographystyle{jneurophys}

@@

Attempts to deduce motor intent in the past have focused on the assumed spring-like properties of human muscles. Springs produce a force according to their impedance and stretch. By measuring force, impedance, and position, Gomi and Kawato\cite{gomi1997human} were able to deduce stretch and thereby infer the muscle's equilibrium point. Supporters of the ``$\lambda$ model''\cite{feldman1995origin} hypothesized that this equilibrium point represented the intent of a movement. Upon Gomi and Kawato's inspection of the equilibrium point as it evolved in time, it was clear that it was highly complex and often not anatomically realizable. Therefore, it could not well-represent the intent of a simple reaching movement. We propose a revised method --- \textit{intent extraction} --- that deduces intended trajectory, even in the face of disturbances. This method describes a class of filters that map a disturbance, process, actuator, and realized trajectory to an intended trajectory. In human reaching, these initial ingredients are available: the process is a dynamic model of the arm, the actuators (muscles) are assumed to act as viscoelastic torque generators, the human interface forces are measured by a sensor, and the realized trajectory is measured.

@@

\section*{Figure Legends}
%\begin{figure}[!ht]
%\begin{center}
%%\includegraphics[width=4in]{figure_name.2.eps}
%\end{center}
%\caption{
%{\bf Bold the first sentence.}  Rest of figure 2  caption.  Caption 
%should be left justified, as specified by the options to the caption 
%package.
%}
%\label{Figure_label}
%\end{figure}

\begin{figure}[!ht]
\begin{center}
%\includegraphics[width=4in]{fig1.eps}
\end{center}
\caption{
{\bf Simulated data illustrating tautology of extraction absent parameter error across pulse and filtered Gaussian noise disturbance types.} Intent is modeled as a minimum jerk, 5th order polynomial. Forces experienced are combined with intent via Burdet et al.'s \cite{burdet2006stability} model to produce the simulated arm trajectory. Extraction to recover intention from arm and force trajectory follows.
}
\label{fig:synthetic}
\end{figure}

\begin{figure}[!ht]
\begin{center}
%\includegraphics[width=4in]{fig2.eps}
\end{center}
\caption{
{\bf Model sensitivity testing (from the variance-based method of Saltelli et al.\cite{saltelli2010variance}) reveals that the model is mostly sensitive to stiffness.} Parameter values are varied in a Sobol-distributed fashion according to Table 1. First order sensitivity, in purple, is the error that would be removed if the parameter was fixed at its nominal value. Total sensitivity, in teal, shows error that would remain if all other parameters were fixed at their nominal values.
}
\label{fig:sensitivity}
\end{figure}

\begin{figure}[!ht]
\begin{center}
%\includegraphics[width=4in]{fig3.eps}
\end{center}
\caption{
{\bf Subjects' disturbed hand trajectories and extraction of intended trajectories from them reveal that both variance and invariance of the motor plan can occur even in response to very large disturbances.} The hand path, in black, deviates from the green baseline, as a force pulse, gray arrows, are applied. This subject's extracted desired trajectories, in red (baseline in faded red), do not significantly differ from baseline during force application, but show some reaction afterwards.
}
\label{fig:anecdotes}
\end{figure}

\begin{figure}[!ht]
\begin{center}
%\includegraphics[width=4in]{fig4.eps}
\end{center}
\caption{
{\bf Comparison of subjects' perpendicular deviations across disturbed and undisturbed conditions reveals that intention is statistically indistinguishable from undisturbed reaching for at least 300 ms.} At most 135 milliseconds after the onset of disturbance, hand deviation in the presence of disturbance (black dots, black band is mean $\pm$ half of the critical value for simultaneous comparisons at 95\% confidence interval) can no longer be explained by undisturbed hand deviation (green band is mean maximum deviation). Movement intention (red dots, band is mean deviation) does not significantly deviate until at least 300 ms after the onset of disturbance.
}
\label{fig:grouptrends}
\end{figure}

>>>>

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}
\usepackage[section]{placeins}

@@

% Bold the 'Figure #' in the caption and separate it with a period
% Captions will be left justified
\usepackage[labelfont=bf,labelsep=period,justification=raggedright]{caption}
%\usepackage[noperiod]{jabbrv}
% Use the PLoS provided bibtex style
\bibliographystyle{plos2009}

@@

Attempts to deduce motor intent in the past have focused on the assumed spring-like properties of human muscles. Springs produce a force according to their impedance and stretch. By measuring force, impedance, and position, Gomi and Kawato\cite{gomi1997human} were able to deduce stretch and thereby infer the muscle's equilibrium point. Supporters of the ``$\lambda$ model''\cite{feldman1995origin} hypothesized that this equilibrium point represented the intent of a movement. Upon Gomi and Kawato's inspection of the equilibrium point as it evolved in time, it was clear that it was highly complex and often not anatomically realizable. Therefore, it could not well-represent the intent of a simple reaching movement. We propose a revised and more general method, \textit{intent extraction}, which calculates the intended trajectory even in the face of disturbances by relating environmental interaction and state to intent. This method affords new ways to 1) test and falsify candidate models of motor control, 2) study the timing and composition of alterations to intent during movement, and 3) understand how intent might be altered by pathology after neural insult. This method describes a class of filters that map a disturbance, process, actuator, and realized trajectory to an intended trajectory. In human reaching, these initial ingredients are available: the process is a dynamic model of the arm, the actuators (muscles) are assumed to act as viscoelastic torque generators, the human interface forces are measured by a sensor, and the realized trajectory is measured.

@@

\pagebreak
\section*{Figures and Figure Legends}
%\begin{figure}[!ht]
%\begin{center}
%%\includegraphics[width=4in]{figure_name.2.eps}
%\end{center}
%\caption{
%{\bf Bold the first sentence.}  Rest of figure 2  caption.  Caption 
%should be left justified, as specified by the options to the caption 
%package.
%}
%\label{Figure_label}
%\end{figure}
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6in]{fig1.png}
\end{center}
\caption{
{\bf Simulated data illustrating tautology of extraction absent parameter error across pulse and filtered Gaussian noise disturbance types.} Intent is modeled as a minimum jerk, 5th order polynomial. Forces experienced are combined with intent via Burdet et al.'s \cite{burdet2006stability} model to produce the simulated arm trajectory. Extraction to recover intention from arm and force trajectory follows.
}
\label{fig:synthetic}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6in]{fig2.png}
\end{center}
\caption{
{\bf Model sensitivity testing (from the variance-based method of Saltelli et al.\cite{saltelli2010variance}) reveals that the model is mostly sensitive to stiffness.} Parameter values are varied in a Sobol-distributed fashion according to Table 1. First order sensitivity, in purple, is the error that would be removed if the parameter was fixed at its nominal value. Total sensitivity, in teal, shows error that would remain if all other parameters were fixed at their nominal values.
}
\label{fig:sensitivity}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6in]{fig3.png}
\end{center}
\caption{
{\bf Subjects' disturbed hand trajectories and extraction of intended trajectories from them reveal that both variance and invariance of the motor plan can occur even in response to very large disturbances.} The hand path, in black, deviates from the green baseline, as a force pulse, gray arrows, are applied. This subject's extracted desired trajectories, in red (baseline in faded red), do not significantly differ from baseline during force application, but show some reaction afterwards.
}
\label{fig:anecdotes}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=4in]{fig4.png}
\end{center}
\caption{
{\bf Comparison of subjects' perpendicular deviations across disturbed and undisturbed conditions reveals that intention is statistically indistinguishable from undisturbed reaching for at least 300 ms.} At most 135 milliseconds after the onset of disturbance, hand deviation in the presence of disturbance (black dots, black band is mean $\pm$ half of the critical value for simultaneous comparisons at 95\% confidence interval) can no longer be explained by undisturbed hand deviation (green band is mean maximum deviation). Movement intention (red dots, band is mean deviation) does not significantly deviate until at least 300 ms after the onset of disturbance.
}
\label{fig:grouptrends}
\end{figure}
